cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-11-28 paper-cardinalR.tex
Added code for table functions

\caption{\label{tab:branching-tb-pdf}cardinalR branching data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_expbranches & Exponential shaped branches.\\
gen\_linearbranches & Linear shaped branches.\\
gen\_curvybranches & Curvy shaped branches.\\
gen\_orglinearbranches & Linear shaped branches originated in one point.\\
gen\_orgcurvybranches & Curvy shaped branches originated in one point.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:cube-tb-pdf}cardinalR cube data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_gridcube & Cube with specified grid points along each axes.\\
gen\_unifcube & Cube with uniform points.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:polynomial-tb-pdf}cardinalR polynomial data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_quadratic & Quadratic pattern.\\
gen\_cubic & Cubic pattern.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:pyramid-tb-pdf}cardinalR pyramid data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_pyrrect & Rectangular-base, with a sharp or blunted apex.\\
gen\_pyrtri & Triangular-base, with a sharp or blunted apex.\\
gen\_pyrstar & Star-shaped base, with a sharp or blunted apex.\\
gen\_pyrfrac & Pyramid with triangular pyramid-shaped holes.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:sphere-tb-pdf}cardinalR sphere data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_circle & Circle.\\
gen\_curvycycle & Curvy cell cycle.\\
gen\_unifsphere & Uniform ball.\\
gen\_hollowsphere & Hollow sphere.\\
gen\_gridedsphere & Grided sphere.\\
gen\_clusteredspheres & Multiple small spheres within a big sphere.\\
gen\_hemisphere & Hemisphere.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:trefoil-tb-pdf}cardinalR trefoil data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_trefoil4d & Trefoil in 4-D.\\
gen\_trefoil3d & Trefoil in 3-D.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:trigonometric-tb-pdf}cardinalR trigonometric data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_crescent & Crescent pattern.\\
gen\_curvycylinder & Curvy cylinder.\\
gen\_sphericalspiral & Spherical spiral.\\
gen\_helicalspiral & Helical spiral.\\
gen\_conicspiral & Conic spiral.\\
gen\_nonlinear & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:noise-tb-pdf}cardinalR noise dimensions generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{10.5cm}}
\toprule
Function & Explanation\\
\midrule
gen\_noisedims & Gaussian noise dimensions with optional mean and standard deviation.\\
gen\_wavydims1 & Wavy noise dimensions based on a user-specified theta sequence with added jitter.\\
gen\_wavydims2 & Wavy noise dimensions using polynomial transformations of an existing dimension vector.\\
gen\_wavydims3 & Wavy noise dimensions using a combination of polynomial and sine transformations based on the first three dimensions of a dataset.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{8.5cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & Möbius-like cluster combined with a Gaussian.\\
make\_multigau & Multiple Gaussian clusters in high-dimensional space.\\
make\_curvygau & Curvilinear cluster with a Gaussian cluster.\\
make\_klink\_circles & K-link circular clusters (non-linear circular patterns).\\
make\_chain\_circles & Chain-like circular clusters connected sequentially.\\
make\_klink\_curvycycle & K-link curvy cycle clusters (curvilinear loop structures).\\
make\_chain\_curvycycle & Chain-like curvy cycle clusters connected sequentially.\\
make\_gaucircles & Circular clusters with a Gaussian cluster in the middle.\\
make\_gaucurvycycle & Curvy circular clusters with a Gaussian in the middle.\\
make\_onegrid & Single grid in two dimensions.\\
make\_twogrid\_overlap & Two overlapping grids.\\
make\_twogrid\_shift & Two grids shifted relative to each other.\\
make\_shape\_para & Parallel shaped clusters.\\
make\_three\_clust\_ & Three clusters with different shapes. (eg:- 01, 02, ..., 20)\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:add-tb-pdf}cardinalR additional functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_bkgnoise & Adds background noise.\\
randomize\_rows & Randomizes the rows of input data.\\
relocate\_clusters & Relocates the clusters.\\
gen\_nproduct & Generates a vector of positive integers whose product is approximately equal to a target value.\\
gen\_nsum & Generates a vector of positive integers whose summation is approximately equal to a target value.\\
normalize\_data & Normalizes data.\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:branching-tb-pdf}cardinalR branching data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_expbranches} & Exponential shaped branches.\\
\texttt{gen\_linearbranches} & Linear shaped branches.\\
\texttt{gen\_curvybranches} & Curvy shaped branches.\\
\texttt{gen\_orglinearbranches} & Linear shaped branches originated in one point.\\
\texttt{gen\_orgcurvybranches} & Curvy shaped branches originated in one point.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:cube-tb-pdf}cardinalR cube data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_gridcube} & Cube with specified grid points along each axes.\\
\texttt{gen\_unifcube} & Cube with uniform points.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:polynomial-tb-pdf}cardinalR polynomial data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_quadratic} & Quadratic pattern.\\
\texttt{gen\_cubic} & Cubic pattern.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:pyramid-tb-pdf}cardinalR pyramid data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_pyrrect} & Rectangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrtri} & Triangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrstar} & Star-shaped base, with a sharp or blunted apex.\\
\texttt{gen\_pyrfrac} & Pyramid with triangular pyramid-shaped holes.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:sphere-tb-pdf}cardinalR sphere data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_circle} & Circle.\\
\texttt{gen\_curvycycle} & Curvy cell cycle.\\
\texttt{gen\_unifsphere} & Uniform ball.\\
\texttt{gen\_hollowsphere} & Hollow sphere.\\
\texttt{gen\_gridedsphere} & Grided sphere.\\
\texttt{gen\_clusteredspheres} & Multiple small spheres within a big sphere.\\
\texttt{gen\_hemisphere} & Hemisphere.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:trefoil-tb-pdf}cardinalR trefoil data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_trefoil4d} & Trefoil in 4-D.\\
\texttt{gen\_trefoil3d} & Trefoil in 3-D.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:trigonometric-tb-pdf}cardinalR trigonometric data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_crescent} & Crescent pattern.\\
\texttt{gen\_curvycylinder} & Curvy cylinder.\\
\texttt{gen\_sphericalspiral} & Spherical spiral.\\
\texttt{gen\_helicalspiral} & Helical spiral.\\
\texttt{gen\_conicspiral} & Conic spiral.\\
\texttt{gen\_nonlinear} & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:noise-tb-pdf}cardinalR noise dimensions generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{10.5cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_noisedims} & Gaussian noise dimensions with optional mean and standard deviation.\\
\texttt{gen\_wavydims1} & Wavy noise dimensions based on a user-specified theta sequence with added jitter.\\
\texttt{gen\_wavydims2} & Wavy noise dimensions using polynomial transformations of an existing dimension vector.\\
\texttt{gen\_wavydims3} & Wavy noise dimensions using a combination of polynomial and sine transformations based on the first three dimensions of a dataset.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{8.5cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{make\_mobiusgau} & Möbius-like cluster combined with a Gaussian.\\
\texttt{make\_multigau} & Multiple Gaussian clusters in high-dimensional space.\\
\texttt{make\_curvygau} & Curvilinear cluster with a Gaussian cluster.\\
\texttt{make\_klink\_circles} & K-link circular clusters (non-linear circular patterns).\\
\texttt{make\_chain\_circles} & Chain-like circular clusters connected sequentially.\\
\texttt{make\_klink\_curvycycle} & K-link curvy cycle clusters (curvilinear loop structures).\\
\texttt{make\_chain\_curvycycle} & Chain-like curvy cycle clusters connected sequentially.\\
\texttt{make\_gaucircles} & Circular clusters with a Gaussian cluster in the middle.\\
\texttt{make\_gaucurvycycle} & Curvy circular clusters with a Gaussian in the middle.\\
\texttt{make\_onegrid} & Single grid in two dimensions.\\
\texttt{make\_twogrid\_overlap} & Two overlapping grids.\\
\texttt{make\_twogrid\_shift} & Two grids shifted relative to each other.\\
\texttt{make\_shape\_para} & Parallel shaped clusters.\\
\texttt{make\_three\_clust\_} & Three clusters with different shapes. (eg:- 01, 02, ..., 20)\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:add-tb-pdf}cardinalR additional functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_bkgnoise} & Adds background noise.\\
\texttt{randomize\_rows} & Randomizes the rows of input data.\\
\texttt{relocate\_clusters} & Relocates the clusters.\\
\texttt{gen\_nproduct} & Generates a vector of positive integers whose product is approximately equal to a target value.\\
\texttt{gen\_nsum} & Generates a vector of positive integers whose summation is approximately equal to a target value.\\
\texttt{normalize\_data} & Normalizes data.\\
\bottomrule
\end{tabular}
\end{table}
